Numerical trajectory patterns of floating macroalgae

### 2020-11-11 thesis_chapter_3.Rmd
tidy up

---
title: 'Numerical trajectory patterns of floating macroalgae'
author: "Ross Coppin"
output:
  pdf_document:
    fig_caption: yes
  html_document:
  word_document:
bibliography: references.bib
csl: markdown/frontiers.csl.txt
---

@@

min_area_path <- ggplot() + 
  geom_path(data = Min_Kfloat_H100_W00_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  geom_path(data = Min_Kfloat_H095_W05_mean,aes(x = lon, y = lat, color = 'blue'), show.legend = FALSE) +
  geom_path(data = Min_Kfloat_H090_W10_mean,aes(x = lon, y = lat, color = 'yellow'), show.legend = FALSE) +
  geom_path(data = Min_Kfloat_H085_W15_mean,aes(x = lon, y = lat, color = 'pink'), show.legend = FALSE) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  ggtitle("Minimum cross-sectional area") + 
  theme_bw()

mean_area_path <- ggplot() + 
  geom_path(data = Mean_Kfloat_H100_W00_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  geom_path(data = Mean_KFloat_H095_W05_mean,aes(x = lon, y = lat, color = 'blue'), show.legend = FALSE) +
  geom_path(data = Mean_KFloat_H090_W10_mean,aes(x = lon, y = lat, color = 'yellow'), show.legend = FALSE) +
  geom_path(data = Mean_KFloat_H085_W15_mean,aes(x = lon, y = lat, color = 'pink'), show.legend = FALSE) +
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  ggtitle("Mean cross-sectional area") + 
  theme_bw()

max_area_path <- ggplot() + 
  geom_path(data = Max_Kfloat_H100_W00_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  geom_path(data = Max_Kfloat_H095_W05_mean,aes(x = lon, y = lat, color = 'blue'), show.legend = FALSE) +
  geom_path(data = Max_Kfloat_H090_W10_mean,aes(x = lon, y = lat, color = 'yellow'), show.legend = FALSE) +
  geom_path(data = Max_Kfloat_H085_W15_mean,aes(x = lon, y = lat, color = 'pink'), show.legend = FALSE) +
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  ggtitle("Maximum cross-sectional area") + 
  theme_bw()

ggarrange(min_area_path, mean_area_path, max_area_path, labels = "AUTO")
```

>>>>

---
title: 'Numerical trajectory patterns of floating macroalgae'
author: "Ross Coppin"
output:
  html_document:
  pdf_document:
    fig_caption: yes
  word_document:
bibliography: references.bib
csl: markdown/frontiers.csl.txt
---

@@

min_area_path <- ggplot() + 
  geom_path(data = Min_Kfloat_H100_W00_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  geom_path(data = Min_Kfloat_H095_W05_mean,aes(x = lon, y = lat, color = 'blue'), show.legend = FALSE) +
  geom_path(data = Min_Kfloat_H090_W10_mean,aes(x = lon, y = lat, color = 'yellow'), show.legend = FALSE) +
  geom_path(data = Min_Kfloat_H085_W15_mean,aes(x = lon, y = lat, color = 'pink'), show.legend = FALSE) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  ggtitle("Minimum cross-sectional area") + 
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

mean_area_path <- ggplot() + 
  geom_path(data = Mean_Kfloat_H100_W00_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  geom_path(data = Mean_KFloat_H095_W05_mean,aes(x = lon, y = lat, color = 'blue'), show.legend = FALSE) +
  geom_path(data = Mean_KFloat_H090_W10_mean,aes(x = lon, y = lat, color = 'yellow'), show.legend = FALSE) +
  geom_path(data = Mean_KFloat_H085_W15_mean,aes(x = lon, y = lat, color = 'pink'), show.legend = FALSE) +
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  ggtitle("Mean cross-sectional area") + 
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

max_area_path <- ggplot() + 
  geom_path(data = Max_Kfloat_H100_W00_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  geom_path(data = Max_Kfloat_H095_W05_mean,aes(x = lon, y = lat, color = 'blue'), show.legend = FALSE) +
  geom_path(data = Max_Kfloat_H090_W10_mean,aes(x = lon, y = lat, color = 'yellow'), show.legend = FALSE) +
  geom_path(data = Max_Kfloat_H085_W15_mean,aes(x = lon, y = lat, color = 'pink'), show.legend = FALSE) +
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  ggtitle("Maximum cross-sectional area") + 
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

ggarrange(min_area_path, mean_area_path, max_area_path, labels = "AUTO")
